---
title: "Assignment 3"
author: "Jaleise Hall"
date: "3/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tibble)
```

### Assignment Details:

- Create a function that contains a *while* loop
- Create another function that uses *case_when*
- Provide an example use of your function in an Rmarkdown document
- Submit on link to github on Gauchospace as usual
- *Remember to use good programming practices; documentation, error-checking, understandable variable names AND go through DataTypes.RM

### While Loop 

```{r}

source("R/tertiary_plants.R")
# Looping when we assume that the number of plants is at least 2650
tertiary_plants(tert = 2650)

#reaches 720 by plant 2667

```


### Case_when Loop

```{r}

source("R/detect_plastic.R")

plastic_table <- tribble(~carbon, ~hydrogen, ~oxygen, ~chlorine,
                         10, 8, 4, 0,
                         10, 8, 4, 0,
                         2, 4, 0, 0,
                         10, 8, 4, 0,
                         20, 6, 5, 2,
                         8, 8, 0, 0,
                         3, 6, 0, 0,
                         8, 8, 0, 0,
                         2, 4, 0, 0,
                         8, 8, 0, 0,
                         2, 3, 0, 1,
                         8, 8, 0, 0,
                         8, 8, 0, 0,
                         8, 8, 0, 0,
                         30, 14, 20, 2,
                         2, 4, 0, 0,
                         2, 4, 0, 0,
                         2, 2, 4, 5,
                         2, 4, 0, 0,)


plastic_table_new <- plastic_table %>% 
  mutate(plastic_type = detect_plastic(C = carbon, H = hydrogen, O = oxygen, Cl = chlorine))

error_table <- tribble(~carbon, ~hydrogen, ~oxygen, ~chlorine,
                         -10, 8, 4, 0,
                         10, -8, 4, 0,
                         2, 4, 0, 0,
                         10, 8, 4, 0,
                         20, 6, -5, 2)

error_table_new <- error_table %>% 
  mutate(plastic_type = detect_plastic(C = carbon, H = hydrogen, O = oxygen, Cl = chlorine))


```

