---
title: "Assignment 2b"
author: "Jaleise Hall"
date: "2/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(tidyverse)
library(purrr)
library(ggpubr)
```


##Calculating power
#Contract:
*Input*: vehicle mass in kg (m), vehicle speed in m/s (V)
*Output*: power in watts (Pb)
*Parameters*: c_rolling (rolling coefficient), g (acceleration due to gravity), A (surface area of vehicle), p_air (air density), and c_drag (aerodynamic resistive coefficient)

#What will the function do?
Compute the power required to keep a car moving at a given speed, as a proxy for automobile fuel efficiency, using the following equation - *body* of the function
$Pb = c_rolling * m * g * V + ½ * A *p_air * c_drag * V^3$
Pb is power in watts, c_rolling is a rolling coefficient, m is vehicle mass in kg, g is acceleration due to gravity, V is vehicle speed in m/s, A is surface area of vehicle in m^2, p_air is air density, and c_drag is an aerodynamic resistive coefficient. 
#Typical values for:
c_rolling = 0.015
c_drag = 0.3
g = 9.8 m/s^2
A = 9 m^2  
p_air = 1.2 mg/m^3


```{r}
#Create car power function
car_fuel_eff = function(m, V, c_rolling = 0.015,  g = 9.8, A = 9, p_air = 1.2, c_drag = 0.3) {
  result =  c_rolling * m * g * V + 0.5 * A *p_air * c_drag * V^3
  return(result) 
}
```

#Compute power given:
m = 31752 kg 
range of vehicle speeds (30 m/s, 80 km/hr, 120 km/hr, 40 km/hr )
Unit conversions: km/hr to m/s, 1 km = 1000m, 1 hr = 3600 s, 1 km/hr = 0.277778 m/s

```{r}
#Create conversion factor for speeds in km/hr
kmhr_ms_conv = 0.2778

#Compute power given range of vehicle speeds
power_30 = car_fuel_eff(m=31752, V=30)
power_22 = car_fuel_eff(m=31752, V=80*kmhr_ms_conv)
power_33 = car_fuel_eff(m=31752, V=120*kmhr_ms_conv)
power_11 = car_fuel_eff(m=31752, V=40*kmhr_ms_conv)

#Results
power_30 
power_22 
power_33 
power_11 
```

```{r}
#Create dataframe to plot

car_fuel_eff_df <- data.frame(power=c(power_30, power_22, power_33, power_11), speed=c(30, 80*kmhr_ms_conv, 120*kmhr_ms_conv, 40*kmhr_ms_conv))

car_fuel_eff_df

```

```{r}
#Create conversion factor for speeds in km/hr
kmhr_ms_conv = 0.2778

#Compute power given range of vehicle speeds
power_75_30 = car_fuel_eff(m=31752*0.75, V=30)
power_75_22 = car_fuel_eff(m=31752*0.75, V=80*kmhr_ms_conv)
power_75_33 = car_fuel_eff(m=31752*0.75, V=120*kmhr_ms_conv)
power_75_11 = car_fuel_eff(m=31752*0.75, V=40*kmhr_ms_conv)

#Results
power_75_30 
power_75_22 
power_75_33 
power_75_11

#Create dataframe to plot

car_fuel_eff_75_df <- data.frame(power=c(power_75_30, power_75_22, power_75_33, power_75_11), speed=c(30, 80*kmhr_ms_conv, 120*kmhr_ms_conv, 40*kmhr_ms_conv))

car_fuel_eff_75_df

```


```{r}
ggplot() +
  labs(x = "Speed (m/s)",
       y = "Power (watts)",
       title = "Vehicle Power as a Function of Speed") +
  geom_line(data=car_fuel_eff_df, 
            aes(x=speed, 
                y=power, 
                color = "black")) +
  geom_line(data=car_fuel_eff_75_df, 
            aes(x=speed, 
                y=power,
                color="red")) +
  scale_x_continuous(limits=c(10,35),
                     breaks=c(10, 20, 30)) +
  scale_color_identity(name = "Vehicle Mass",
                          breaks = c("black", "red"),
                          labels = c("Mass = 31752 kg", "Mass = 23814 kg"),
                          guide = "legend") +
  theme_bw()
  

```


```{r}

source("assignments/assignment2a/assignment2a.R")

nsample = 100
crolling = runif(min=0.01, max=0.03, n=100)

maxrolling=0.01
for ( i  in 1:length(maxrolling)) {
  maxrolling = ifelse(crolling[i] > maxrolling, crolling[i], maxrolling)
}

maxrolling

```

# Our highway

2 car types 

Imagine with have 3 different car types - and we know how often each occurs:

* car A  mass 31752 kg, area 9 m^2^

* car B mass 30000 kg, area 10 m^2^

Mean highway speed is 120 km/hr 

```{r}

# generate a structure to store info on our possible cars
possible_cars = data.frame(name = c("A","B"),mass=c(31752,30000), area = c(9,10))

# first look at how results vary for mean speed say 100km/hr
# do conversion
speed_base = 120 * kmhr_ms_conv

# because I have one mass and area for each car and only 1 speed
# I can estimate power for each car type
# add to the data structure
possible_cars$power = car_fuel_eff(V=speed_base, A = possible_cars$area, m=possible_cars$mass)

head(possible_cars)

# show results                         
ggplot(possible_cars, aes(x=mass, y=power, fill=as.factor(area)))+geom_col()+labs(y="Power W", x="Mass (kg)")

```

# Building a highway

What could be the total power consumed if there are 100 cars on this highway each hour,
they are travelling at a range of speeds - mean is 100km/hr and speeds tend to
be log-normally distributed)

How would the total power consumed vary by car
So if all cars are car A; OR all cars are car B OR all cars are car C

We will use *sample* here to generate speeds for our 100 cars and look at different ways to
repeat power calculation for different cars

* repeating by hand
* *pmap* for repetition - a efficient way of looping in R
* *for* for repetition - a more standard way of looping available in many langugaes

# First lets do it 'by hand'

```{r}

# what is I want to estimate average power use given  each car

possible_cars

# use sample to generate a distribution of speeds

# assume a log normal distribution of speeds with mean 100km/hr
# recall our function needs speed in m/s not km/hr so we will also do a conversion
# lets get a sample of a 200 speeds- we could also do this by actually measuring speeds

nsample = 100

crollings = rlnorm(mean=crolling, sd=0.1*crolling, nsample)
summary(crollings)

plot(density(crollings), ylab="Distribution of Rolling Coefficients")


# how do we run each car for all speeds 

# first lets to it by hand for the first car - the first row in our possible cars matrix
possible_cars[1,]

# we could do it by hand
powerA = car_fuel_eff(c_rolling = crollings, V=120*kmhr_ms_conv, A = possible_cars$area[1], m=possible_cars$mass[1])
# lets look at what we get
summary(powerA)

# next car (row 2)
powerB = car_fuel_eff(c_rolling = crollings, V = 120*kmhr_ms_conv, A = possible_cars$area[2], m=possible_cars$mass[2])
# lets look at what we get
summary(powerB)

# we could put this together
powerall1 = cbind.data.frame(powerA, powerB)
colnames(powerall1)=possible_cars$name


# for plotting sometimes its useful to turn columns in to rows
powerallr1 = powerall1 %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(powerallr1)

# quick visualization
# lets save it so that we can compare
method1_plot = ggplot(powerallr1, aes(car, power, fill=car))+geom_boxplot()+ggtitle("By Hand")
method1_plot

```


# Using `pmap()`

```{r}

possible_cars

# assume a log normal distribution of speeds with mean 100km/hr
# recall our function needs speed in m/s not km/hr so we will also do a conversion
# lets get a sample of a 200 speeds- we could also do this by actually measuring speeds

nsample = 100

crollings2 = rlnorm(mean=crolling, sd=0.1*crolling, nsample)
summary(crollings2)

plot(density(crollings2), ylab="Distribution of Rolling Coefficients")


# how do we run each car for all speeds 
# pmap runs a function for each value in a list of parameters, with other parameters set for each iteration


powerall2 = pmap(list(A = possible_cars$area, m=possible_cars$mass), car_fuel_eff, V=120*kmhr_ms_conv, c_rolling = crollings2)

# lets turn to a data frame for easier graphing
# we can add column names
powerall2 = as.data.frame(powerall2, col.names=possible_cars$name)

# apply family of functions does this to - FYI
# what mapply does is run the function for each row in parameters listed, using values for other parameters listed in MoreArgs EACH time - a column for row in parameter list is returned
powerall2b = mapply(FUN=autopower, A = possible_cars$area, m=possible_cars$mass, MoreArgs = list(V=speeds)  )
# we can add column names
colnames(powerall2b)=possible_cars$name

head(powerall2b)
head(powerall2)


# for plotting sometimes its useful to turn columns in to rows
powerallr2 = powerall2 %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(powerallr2)

# quick visualization

method2_plot = ggplot(powerallr2, aes(car,power, fill=car))+geom_boxplot()+ggtitle("pmap")
method2_plot

# put plots side by side
# to confirm that they look similar
ggarrange(method1_plot, method2_plot)

# compare values
head(powerallr2)
head(powerallr1)

# not exactly the same - why?
# recall that we sample speeds!

# but we can compare means (also using  map :)
# map runs the function (here - mean), over each column 
# they are close but still not exact, so statistics such as means and quantiles are # similar, and relative difference between cars is the same
powerall1 %>% map(mean)
powerall2 %>% map(mean)

# upper 90% quantile
powerall1 %>% map(quantile, probs=0.9)
powerall2 %>% map(quantile, probs=0.9)

```






