---
title: "Assignment 2a"
author: "Becca Reynolds"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
```


##Calculating power
#Contract:
*Input*: vehicle mass in kg (m), vehicle speed in m/s (V)
*Output*: power in watts (Pb)
*Parameters*: c_rolling (rolling coefficient), g (acceleration due to gravity), A (surface area of vehicle), p_air (air density), and c_drag (aerodynamic resistive coefficient)

#What will the function do?
Compute the power required to keep a car moving at a given speed, as a proxy for automobile fuel efficiency, using the following equation - *body* of the function
$Pb = c_rolling * m * g * V + ½ * A *p_air * c_drag * V^3$
Pb is power in watts, c_rolling is a rolling coefficient, m is vehicle mass in kg, g is acceleration due to gravity, V is vehicle speed in m/s, A is surface area of vehicle in m^2, p_air is air density, and c_drag is an aerodynamic resistive coefficient. 
#Typical values for:
c_rolling = 0.015
c_drag = 0.3
g = 9.8 m/s^2
A = 9 m^2  
p_air = 1.2 mg/m^3


```{r}
#Create car power function
car_fuel_eff = function(m, V, c_rolling = 0.015,  g = 9.8, A = 9, p_air = 1.2, c_drag = 0.3) {
  result =  c_rolling * m * g * V + 0.5 * A *p_air * c_drag * V^3
  return(result) 
}
```

#Compute power given:
m = 31752 kg 
range of vehicle speeds (30 m/s, 80 km/hr, 120 km/hr, 40 km/hr )
Unit conversions: km/hr to m/s, 1 km = 1000m, 1 hr = 3600 s, 1 km/hr = 0.277778 m/s

```{r}
#Create conversion factor for speeds in km/hr
kmhr_ms_conv = 0.2778

#Compute power given range of vehicle speeds
power_30 = car_fuel_eff(m=31752, V=30)
power_22 = car_fuel_eff(m=31752, V=80*kmhr_ms_conv)
power_33 = car_fuel_eff(m=31752, V=120*kmhr_ms_conv)
power_11 = car_fuel_eff(m=31752, V=40*kmhr_ms_conv)

#Results
power_30 
power_22 
power_33 
power_11 
```

```{r}
#Create dataframe to plot

car_fuel_eff_df <- data.frame(power=c(power_30, power_22, power_33, power_11), speed=c(30, 80*kmhr_ms_conv, 120*kmhr_ms_conv, 40*kmhr_ms_conv))

car_fuel_eff_df

```

```{r}
#Create conversion factor for speeds in km/hr
kmhr_ms_conv = 0.2778

#Compute power given range of vehicle speeds
power_75_30 = car_fuel_eff(m=31752*0.75, V=30)
power_75_22 = car_fuel_eff(m=31752*0.75, V=80*kmhr_ms_conv)
power_75_33 = car_fuel_eff(m=31752*0.75, V=120*kmhr_ms_conv)
power_75_11 = car_fuel_eff(m=31752*0.75, V=40*kmhr_ms_conv)

#Results
power_75_30 
power_75_22 
power_75_33 
power_75_11

#Create dataframe to plot

car_fuel_eff_75_df <- data.frame(power=c(power_75_30, power_75_22, power_75_33, power_75_11), speed=c(30, 80*kmhr_ms_conv, 120*kmhr_ms_conv, 40*kmhr_ms_conv))

car_fuel_eff_75_df

```


```{r}
ggplot() +
  labs(x = "Speed (m/s)",
       y = "Power (watts)",
       title = "Vehicle Power as a Function of Speed") +
  geom_line(data=car_fuel_eff_df, 
            aes(x=speed, 
                y=power, 
                color = "black")) +
  geom_line(data=car_fuel_eff_75_df, 
            aes(x=speed, 
                y=power,
                color="red")) +
  scale_x_continuous(limits=c(10,35),
                     breaks=c(10, 20, 30)) +
  scale_color_identity(name = "Vehicle Mass",
                          breaks = c("black", "red"),
                          labels = c("Mass = 31752 kg", "Mass = 23814 kg"),
                          guide = "legend") +
  theme_bw()
  

```


